### 2022-09-28 ersteops/templates/printpdf/paperless_template.tex
add medications solution to template

>>>>

    {% for item in content.json_medications_solution %}
      {% if forloop.counter0 == 0 %}
          \put(0.04964403,0.32745002){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
          \put(0.11108429,0.32756971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
      {% endif %}
      {% if forloop.counter0 == 1 %}
          \put(0.04964403,0.31750983){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
          \put(0.11108429,0.31762951){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
      {% endif %}
      {% if forloop.counter0 == 2 %}
          \put(0.04964403,0.30867309){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
          \put(0.11108429,0.30879277){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
      {% endif %}
    {% endfor %}

    {{ content.medications }}
